Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-28 paper/ms.tex
latex column width

\subsubsection{Not SB2}
We derived limits on blended spectroscopic companions using the
stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, the
spectra would have revealed companions with flux fractions $F_2/F_1
\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
% For bound companions this is justified through reasoning that coeval
% binary companions to \tn\ would have both longer rotation periods and
% smaller stellar radii. The equatorial velocities of such companions
% would therefore be expected to be smaller than that of \tn.

@@

The easiest path towards definitively confirming the planetary
nature of \tn\ will be a Rossiter-McLaughlin (RM) measurement.  Detection of
an RM signal consistent with the photometric transit would rule out
BEB and HEB scenarios, as it would imply that the eclipsing object is
bound to the target star. Combined with our non-detection of the
planet's mass from radial velocity monitoring, this would confirm that
\pn\ is a planet.

>>>>

\subsubsection{Not SB2}
We derived limits on blended spectroscopic companions using the
stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, the
spectra would have revealed companions with flux fractions $F_2/F_1
\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).

@@

The easiest way to definitively confirm the planetary nature of \tn\
will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
signal consistent with the photometric transit would rule out BEB and
HEB scenarios, as it would imply that the eclipsing object is bound to
the target star. Combined with our non-detection of the planet's mass
from radial velocity monitoring, this would confirm that \pn\ is a
planet.
